```{r include = FALSE}
showWarnings = FALSE

library(tableHTML)
library(yaml)
library(magick)
library(pdftools)
library(knitr)
library(miscTools)
library(plyr) 
library(DT) 
library(dplyr) 

configs = 'configs/'
proj_info <- read_yaml(paste0(configs,'local_configs.yaml'))

project <- proj_info$`PROJECT`   
organism <- proj_info$`ORGANISM`
sequencing <- proj_info$`SEQUENCING`
method <- proj_info$`METHOD`
resolution <- proj_info$`RESOLUTION`
matrix <- proj_info$`MATRIX`
resolution <- proj_info$`RESOLUTION`
mito <- proj_info$`MITO`
mito_regression <- proj_info$`MITO_REGRESSION`
resolution <- proj_info$`RESOLUTION`
conserved_genes <- proj_info$`CONSERVED_GENES`

if (proj_info$METHOD == 'ALL') 
{
  proj_info$METHODS <- c('RPCA', 'SCT', 'Standard')
} else {
  proj_info$METHOD <- c(proj_info$METHOD)
}

methods <- proj_info$METHODS
resolution <- as.list(strsplit(resolution, ' '))[[1]]
```
---
title: `r toupper(project)` Project
date: '`r Sys.Date()`'
output: pdf_document
---

### User Parameter Overview
Organism: `r proj_info$ORGANISM`   
Integration Method(s): `r proj_info$METHODS`     
Resolution(s): `r proj_info$RESOLUTION`   
Starting 10X Data Format: `r proj_info$MATRIX`   
Initial Principal Components: `r proj_info$ICOMPONENTS`   
Storage Method: `r proj_info$STORAGE`    
Mitochondria Threshold: `r proj_info$MITO`    
Mitochondria Regression: `r proj_info$MITO_REGRESSION`   
Minimum Feature Threshold: `r proj_info$MIN_FEATURE_THRESHOLD`   
Maximum Feature Threshold: `r proj_info$MAX_FEATURE_THRESHOLD`   
Cell Cycling Regression: `r proj_info$CCREGRESSION`    
Cell Cycling Regression Method: `r proj_info$CCREGRESSION_METHOD`   
Calculate Conserved Genes: `r proj_info$CONSERVED_GENES`   
Annotation Marker Threshold: `r proj_info$MARKER_THRESHOLD`    
User Supplied Marker File(s): `r proj_info$USER_GENE_FILE`   

```{r include = FALSE}

html_output_dir <- paste0('html_report_', project, '/')
sample_list <- read.csv('samples.sample_list', sep = '\t')
project_dir <- paste0('data/endpoints/', project, '/')
estimate_list_10X <- c()
estimate_list_DF <- c()

sample_links <- c()
for(s in sample_list[,1]) 
{
  sample_links <- append(sample_links, paste0('[', s, ']', '(', html_output_dir, s, '.html)'))
  
  barcode_10X <- paste0(project_dir, s, '/10X/outs/barcodes.tsv.gz')
  wc_10X <- paste0('zcat < ', barcode_10X, ' | wc -l')
  #Note: Linux == wc_10X <- paste0('zcat ', barcode_10X, ' | wc -l')
  estimate_list_10X <- append(estimate_list_10X, system(wc_10X, intern=TRUE))
  
  barcode_doubletF <- paste0(project_dir, s, '/doubletFinder/barcodes.tsv.gz')
  wc_DF <- paste0('zcat < ', barcode_doubletF, ' | wc -l')
  estimate_list_DF <- append(estimate_list_DF, system(wc_DF, intern=TRUE))
}

samples_display <- data.frame(Name = sample_links, Experimental_Condition = sample_list[,2], Initial_Cell_Count = estimate_list_10X, PostDF_Cell_Count=estimate_list_DF)

figures_dir <- paste0(project_dir, 'analysis/figures/')
qc1 <- image_read_pdf(paste0(figures_dir,'qc_1.pdf'))
qc2 <- image_read_pdf(paste0(figures_dir,'qc_2.pdf'))
elbow <- image_read_pdf(paste0(figures_dir, project, '_elbow_plot.pdf'))
```

### Data Overview

### Samples:
***
```{r echo = FALSE}
kable(samples_display, align = "c", format = "html", table.attr = "style='width:70%;'")
```
###### PostDF_Cell_Count: DF == DoubletFinder
***

### QC
#### Initial QC:
***

```{r echo = FALSE, message = FALSE, out.height='50%', out.width='80%'}
print(qc1[1], info=F)
```

#### Post Filtering QC:
***

```{r echo = FALSE, message = FALSE, out.height='50%', out.width='80%'}
print(qc2, info=F)
```

```{r include=FALSE}
sig <- read.csv(paste0(project_dir, 'analysis/tables/sigPC.txt'), sep='', header=T)
sigPC <- sig$x
```
***

## Analysis
#### Elbow Plot: 
##### `r sigPC` Components Selected    

```{r echo = FALSE, message = FALSE, out.height='50%', out.width='80%'}
print(elbow, info=F)
```

```{r include = FALSE}

cluster_file_name <- '_clusterProportions_integrated_snn_res.'

if (proj_info$RESOLUTION == 'I') {
  res <- c(0.5, 0.8, 1.2)
} else if (proj_info$RESOLUTION != 0) {
  res <- c(proj_info$RESOLUTION)
  } else {
  res <- c(0.8)
  }

res <- as.list(strsplit(res, ' ')[[1]])
res[3] <- '1'

#list of methods
method_col <- c()
i <- 1
for(m in methods) {
  for(r in res) {
    method_col[i] <- m
    i <- i + 1
  }
}

#list of resolutions (for each method)
res_col <- c()
j <- 1
for(m in methods) {
  for(r in res) {
    res_col[j] <- r
    j <- j + 1
  }
}

lappend <- function (lst, ...){
lst <- c(lst, list(...))
  return(lst)
}

list_vars <- list()
k <- 1
for(m in methods) {
  filepath <- paste(project_dir, '/analysis/PCA_', sigPC, '/tables/dge_plots/', m, '/', project,  cluster_file_name, sep = '')
  for(r in res) {
    file <- read.csv(paste0(filepath, r, '_', m, '.txt'), sep = '\t', header = TRUE)
    print(file)
    sizes <- 
    list_vars <- lappend(list_vars, file[1,])
    k <- k + 1
  }
}

 max_ncol <- 0
 for(l in list_vars) {
   max_ncol <- max(max_ncol, ncol(l))
 }
 
 eqlength_list_vars <- list()
 for(l in list_vars) {
   if(ncol(l) < max_ncol) {
     diff <- max_ncol - ncol(l)
     for(t in 1:diff) {
       new <- c('NA')
       l[ , ncol(l) + 1] <- new
       colnames(l)[ncol(l)] <- paste0('X', ncol(l) - 1)
     }
   }
   eqlength_list_vars <- lappend(eqlength_list_vars, l)
 }
 
 cluster_proportions <- data.frame(matrix(NA, ncol = max_ncol, nrow = i - 1))
 r <- 1
 for(l in eqlength_list_vars) {
   cluster_proportions[r,] <- l[1,]
   r <- r + 1
 }
 
resmet <- cbind(method_col, res_col)
 
resmetclusters <- cbind(resmet, cluster_proportions)
 
resmetclusters$pdf <-  paste0('[Cluster Plots](', project_dir, 'analysis/PCA_', sigPC, '/figures/dge_plots/', resmetclusters$method_col, '/', project, '_clusterProportions_integrated_snn_res.', resmetclusters$res_col, '_', resmetclusters$method_col, '.pdf)')

new_df <- resmetclusters %>% select('pdf', everything())
resmetclusters <- new_df %>% select('method_col', everything())
```
***

### List of All Output
```{r echo = F}
output_file = noquote(paste0('html_report_', project, '/', project, '_file_list.html'))

##### Text files located here: `r paste0(project_dir, 'analysis/PCA_', sigPC, '/tables/dge_plots/METHOD/')`  
##### Figure files located here: `r paste0(project_dir, 'analysis/PCA_', sigPC, '/figures/dge_plots/METHOD/')`
```

#### [Project Output File List](`r output_file`)

### Cluster Proportions
***
Text files location: data/endpoints/project_name/analysis/PCA_\*/tables/dge_plots/METHOD/     
Figure files location: data/endpoints/project_name/analysis/PCA_\*/figures/dge_plots/METHOD/   

***

```{r echo = FALSE, out.width='60%'}
kable(resmetclusters)
```