---
#showWarnings = FALSE
output: html_document
runtime: shiny
---
```{r include = FALSE}
library(tableHTML)
library(yaml)
library(magick)
library(pdftools)
library(knitr)
library(miscTools)
library(plyr) 
library(DT) 
library(dplyr) 

configs = 'configs/'
proj_info <- read_yaml(paste0(configs,'local_configs.yaml'))

project <- proj_info$`PROJECT`   
organism <- proj_info$`ORGANISM`
sequencing <- proj_info$`SEQUENCING`
method <- proj_info$`METHOD`
resolution <- proj_info$`RESOLUTION`
matrix <- proj_info$`MATRIX`
resolution <- proj_info$`RESOLUTION`
mito <- proj_info$`MITO`
mito_regression <- proj_info$`MITO_REGRESSION`
resolution <- proj_info$`RESOLUTION`

if (proj_info$METHOD == 'ALL') 
{
  proj_info$METHODS <- c('RPCA', 'SCT', 'Standard')
} else {
  proj_info$METHOD <- c(proj_info$METHOD)
}

methods <- proj_info$METHODS
```
---
title: `r toupper(project)` Project
date: '`r Sys.Date()`'
---

### User Parameter Overview
Organism: `r proj_info$ORGANISM`   
Integration Method(s): `r proj_info$METHODS`     
Resolution(s): `r proj_info$RESOLUTION`   
Starting 10X Data Format: `r proj_info$MATRIX`   
Initial Principal Components: `r proj_info$ICOMPONENTS`   
Storage Method: `r proj_info$STORAGE`    
Mitochondria Threshold: `r proj_info$MITO`    
Mitochondria Regression: `r proj_info$MITO_REGRESSION`   
Minimum Feature Threshold: `r proj_info$MIN_FEATURE_THRESHOLD`   
Maximum Feature Threshold: `r proj_info$MAX_FEATURE_THRESHOLD`   
Cell Cycling Regression: `r proj_info$CCREGRESSION`    
Cell Cycling Regression Method: `r proj_info$CCREGRESSION_METHOD`   
Annotation Marker Threshold: `r proj_info$MARKER_THRESHOLD`    
User Supplied Marker File(s): `r proj_info$USER_GENE_FILE`   

```{r include = FALSE}

sample_list <- read.csv('samples.sample_list', sep = '\t')
estimate_list <- read.csv(paste0('html_report_', project, '/estimates.txt'), header=F, sep = '\t')

sample_links <- c()
for(s in sample_list[,1]) 
{
  #sample_links <- append(sample_links, paste0('<a href=\"', s,'.html\">',s,'</a>'))
  #sample_links <- append(sample_links, paste0('[', s, ']', '(', s, '.html)'))
  sample_links <- append(sample_links, paste0('[', s, ']', '(html_report_', project, '/', s, '.html)'))
}

samples_display <- data.frame(Name = sample_links, Experimental_Condition = sample_list[,2], Initial_Cell_Count = estimate_list$V2)

#samples_display$Initial_Cell_Count <- paste0(samples_display$Initial_Cell_Count, '/outs/html.summary')
figures_dir <- 'data/endpoints/pastor/analysis/figures/'
qc1 <- image_read_pdf(paste0(figures_dir,'qc_1.pdf'))
qc2 <- image_read_pdf(paste0(figures_dir,'qc_2.pdf'))
elbow <- image_read_pdf(paste0(figures_dir,'pastor_elbow_plot.pdf'))
```

### Data Overview

### Samples:
***
```{r echo = FALSE}
#datatable(samples_display)
kable(samples_display, align = "c", format = "html", table.attr = "style='width:70%;'")
```
***

### QC
#### Initial QC:
***
```{r echo = FALSE, message = FALSE, out.height='50%', out.width='80%'}
print(qc1[1], info=F)
```
***

#### Post Filtering QC:
***
```{r echo = FALSE, message = FALSE, out.height='50%', out.width='80%'}
print(qc2, info=F)
```
***

```{r include=FALSE}
sig <- read.csv(paste0('data/endpoints/', project, '/analysis/tables/sigPC.txt'), sep='', header=T)
sigPC <- sig$x
```
***

## Analysis
#### Elbow Plot: 
##### `r sigPC` Components Selected
```{r echo = FALSE, message = FALSE, out.height='50%', out.width='80%'}
print(elbow, info=F)
```

```{r include = FALSE}

cluster_file_name <- '_clusterProportions_integrated_snn_res.'
folder = paste0('data/endpoints/', project, '/')

if (proj_info$RESOLUTION == 'I') {
  res <- c(0.5, 0.8, 1.2)
} else if (proj_info$RESOLUTION != 0) {
  res <- c(proj_info$RESOLUTION)
  } else {
  res <- c(0.8)
  }

res <- as.list(strsplit(res, ' ')[[1]])
res[3] <- '1'

#list of methods
method_col <- c()
i <- 1
for(m in methods) {
  for(r in res) {
    method_col[i] <- m
    i <- i + 1
  }
}

#list of resolutions (for each method)
res_col <- c()
j <- 1
for(m in methods) {
  for(r in res) {
    res_col[j] <- r
    j <- j + 1
  }
}

lappend <- function (lst, ...){
lst <- c(lst, list(...))
  return(lst)
}

list_vars <- list()
k <- 1
for(m in methods) {
  filepath <- paste(folder, '/analysis/PCA_', sigPC, '/tables/dge_plots/', m, '/', project,  cluster_file_name, sep = '')
  for(r in res) {
    file <- read.csv(paste0(filepath, r, '_', m, '.txt'), sep = '\t', header = TRUE)
    print(file)
    sizes <- 
    list_vars <- lappend(list_vars, file[1,])
    k <- k + 1
  }
}

 max_ncol <- 0
 for(l in list_vars) {
   max_ncol <- max(max_ncol, ncol(l))
 }
 
 eqlength_list_vars <- list()
 for(l in list_vars) {
   if(ncol(l) < max_ncol) {
     diff <- max_ncol - ncol(l)
     for(t in 1:diff) {
       new <- c('NA')
       l[ , ncol(l) + 1] <- new
       colnames(l)[ncol(l)] <- paste0('X', ncol(l) - 1)
     }
   }
   eqlength_list_vars <- lappend(eqlength_list_vars, l)
 }
 
 cluster_proportions <- data.frame(matrix(NA, ncol = max_ncol, nrow = i - 1))
 r <- 1
 for(l in eqlength_list_vars) {
   cluster_proportions[r,] <- l[1,]
   r <- r + 1
 }
 
resmet <- cbind(method_col, res_col)
 
resmetclusters <- cbind(resmet, cluster_proportions)
 
resmetclusters$pdf <-  paste0('[Cluster Plots](data/endpoints/', project, '/analysis/PCA_', sigPC, '/figures/dge_plots/', resmetclusters$method_col, '/pastor_clusterProportions_integrated_snn_res.', resmetclusters$res_col, '_', resmetclusters$method_col, '.pdf)')

new_df <- resmetclusters %>% select('pdf', everything())
resmetclusters <- new_df %>% select('method_col', everything())
```
***

### List of All Output
```{r echo = F}
output_file = noquote(paste0('html_report/', project, '_file_list.html'))
```

[Project Output File List](`r output_file`)

### Cluster Proportions
##### Text files located here: `r paste0('data/endpoints/', project, '/analysis/PCA_', sigPC, '/tables/dge_plots/METHOD/')`  
##### Figure files located here: `r paste0('data/endpoints/', project, '/analysis/PCA_', sigPC, '/figures/dge_plots/METHOD/')`

```{r echo = FALSE, out.width='60%'}
#datatable(resmetclusters)
kable(resmetclusters)
```

```{r setup, warnings=FALSE, echo=FALSE}
# Set up
suppressPackageStartupMessages(library(Seurat))
suppressPackageStartupMessages(library(shiny))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(rsconnect))
suppressPackageStartupMessages(library(magick))

proj_name <- "data/endpoints/pastor/"

dir.create(paste0('html_report/compare_images'))

res_choices <- c(0.6, 0.8, 1.0, 1.2)
method_choices <- c("RPCA", "SCT", "Standard")

shinyApp(
  
  ui <- fluidPage(
    h2("Plots"),
    h6('Figure files located here: data/endpoints/project_name/analysis/PCA_*/figures/dge_plots/METHOD/project_initial_cluster_plots_integrated_snn_res.RESOLUTION_METHOD.pdf'),
    h5('A method and resolution must be selected before any figures will appear. This step may take several minutes to appear.'),
    fluidRow(
      column(4, 
             selectInput("method1", label = "Method for Plot 1:",
                choices = method_choices),
             selectInput("res1", label = "Resolution for Plot 1:",
                choices = res_choices)),
      column(4,
             selectInput("method2", label = "Method for Plot 2:",
                choices = method_choices),
             selectInput("res2", label = "Resolution for Plot 2:",
                choices = res_choices)),
      column(4,
             selectInput("method3", label = "Method for Plot 3:",
                choices = method_choices),
             selectInput("res3", label = "Resolution for Plot 3:",
                choices = res_choices))
    ),
    fluidRow(
      column(4, imageOutput('plot1', width = "auto")),
      column(4, imageOutput('plot2', width = "auto")),
      column(4, imageOutput('plot3', width = "auto"))
    ),
    h2('Tables'),
    h6('Text files located here: data/endpoints/project_name/analysis/PCA_*/tables/dge_plots/METHOD/project_name_markers_integrated_snn_res.RESOLUTION_METHOD.txt'),
    h5('To look at a certain cluster of a resolution and method, enter the appropriate cluster number. If the entered number is negative, a table with all cluster numbers will be displayed. If a postive but invalid cluster number is entered, no table will be displayed.'),
 
    fluidRow(
      column(3, 
             numericInput('cluster1', 'Cluster number from plot 1', value = -1, min = 0, max = 100)),
      column(3, offset = 1, 
             numericInput('cluster2', 'Cluster number from plot 2', value = -1, min = 0, max = 100)),
      column(3, offset = 1, 
             numericInput('cluster3', 'Cluster number from plot 3', value = -1, min = 0, max = 100))
    ),
    fluidRow(
      column(3,
             dataTableOutput('top100_bycluster_tbl1')
             ),
      column(3, offset = 1,
             dataTableOutput('top100_bycluster_tbl2')
             ),
      column(3, offset = 1,
             dataTableOutput('top100_bycluster_tbl3')
             )
    )
  ),
  
  
  server <- function(input, output) {
    
    output$plot1 <- renderImage({
      doublet_pages<-image_read_pdf(paste0(proj_name,'/analysis/PCA_12/figures/dge_plots/', 
                                        input$method1, '/pastor_initial_cluster_plots_integrated_snn_res.', 
                                        input$res1, '_', input$method1, '.pdf'))
      doublet_pages[7] %>% image_write(., path = paste0('html_report/compare_images/', input$method1, input$res1, '_image.png'), format = 'png')
    
      list(src = paste0('html_report/compare_images/', input$method1, input$res1, '_image.png'),
         alt = paste(input$method1, input$res1), width = 250, height = 250)

      }, deleteFile = TRUE)

    
    output$plot2 <- renderImage({
      doublet_pages<-image_read_pdf(paste0(proj_name,'/analysis/PCA_12/figures/dge_plots/', 
                                        input$method2, '/pastor_initial_cluster_plots_integrated_snn_res.', 
                                        input$res2, '_', input$method2, '.pdf'))
      doublet_pages[7] %>% image_write(., path = paste0('html_report/compare_images/', input$method2, input$res2, '_image.png'), format = 'png')
    
      list(src = paste0('html_report/compare_images/', input$method2, input$res2, '_image.png'),
         alt = paste(input$method2, input$res2), width = 250, height = 250)

      }, deleteFile = TRUE)
    
    
    output$plot3 <- renderImage({
       doublet_pages<-image_read_pdf(paste0(proj_name,'/analysis/PCA_12/figures/dge_plots/', 
                                        input$method3, '/pastor_initial_cluster_plots_integrated_snn_res.', 
                                        input$res3, '_', input$method3, '.pdf'))
      doublet_pages[7] %>% image_write(., path = paste0('html_report/compare_images/', input$method3, input$res3, '_image.png'), format = 'png')
    
      list(src = paste0('html_report/compare_images/', input$method3, input$res3, '_image.png'),
         alt = paste(input$method3, input$res3), width = 250, height = 250)

      }, deleteFile = TRUE)
    
    col_names <- c('avg_log2FC', 'p_val_adj', 'cluster', 'gene')
    new_col_names <- c('log', 'pval', 'cl.', 'gene')
    
    output$top100_bycluster_tbl1 <- renderDataTable({
      orig_top100tbl_1 <- read.table(paste0(proj_name, '/analysis/PCA_12/tables/dge_plots/', input$method1, '/pastor_top100_markers_integrated_snn_res.', input$res1,'_', input$method1, '.txt'), header=TRUE, sep='\t')
      orig_top100tbl_1$avg_log2FC <- signif(orig_top100tbl_1$avg_log2FC,3)
      orig_top100tbl_1$p_val_adj <- signif(orig_top100tbl_1$p_val_adj,3)
      disp_top100tbl_1 <- orig_top100tbl_1[,col_names]
      colnames(disp_top100tbl_1) <- new_col_names
      vec <- c(input$cluster1)
      
      if(input$cluster1<0) {
        datatable(disp_top100tbl_1, rownames = FALSE, width = 100)
      } else {
        subtable1 <- disp_top100tbl_1[disp_top100tbl_1$cl %in% vec,]
        datatable(subtable1, rownames = FALSE, width = 100)
      }
    })
    
    output$top100_bycluster_tbl2 <- renderDataTable({
      
      orig_top100tbl_2 <- read.table(paste0(proj_name,'/analysis/PCA_12/tables/dge_plots/', input$method2,'/pastor_top100_markers_integrated_snn_res.', input$res2,'_', input$method2,'.txt'), header=TRUE, sep='\t')
      
      orig_top100tbl_2$avg_log2FC <- signif(orig_top100tbl_2$avg_log2FC,3)
      orig_top100tbl_2$p_val_adj <- signif(orig_top100tbl_2$p_val_adj,3)
      disp_top100tbl_2 <- orig_top100tbl_2[,col_names]
      colnames(disp_top100tbl_2) <- new_col_names
      vec <- c(input$cluster2)
      
      if(input$cluster2<0) {
        datatable(disp_top100tbl_2, rownames = FALSE, width = 100)
      } else {
        subtable2 <- disp_top100tbl_2[disp_top100tbl_2$cl %in% vec,]
        datatable(subtable2, rownames = FALSE, width = 100)
      }
    })
    
    output$top100_bycluster_tbl3 <- renderDataTable({
      orig_top100tbl_3 <- read.table(paste0(proj_name,'/analysis/PCA_12/tables/dge_plots/', input$method3,'/pastor_top100_markers_integrated_snn_res.', input$res3,'_', input$method3,'.txt'), header=TRUE, sep='\t')
      
      orig_top100tbl_3$avg_log2FC <- signif(orig_top100tbl_3$avg_log2FC,3)
      orig_top100tbl_3$p_val_adj <- signif(orig_top100tbl_3$p_val_adj,3)
      disp_top100tbl_3 <- orig_top100tbl_3[,col_names]
      colnames(disp_top100tbl_3) <- new_col_names
      vec <- c(input$cluster3)
      
      if(input$cluster3<0) {
        datatable(disp_top100tbl_3, rownames = FALSE, width = 100)
      } else {
        subtable3 <- disp_top100tbl_3[disp_top100tbl_3$cl %in% vec,]
        datatable(subtable3, rownames = FALSE, width = 100)
      }
      
    })
   },
  options = list(width = "100%", height=1000)      
 )
```



